\keys{Mobile, Web, Rest, RestFul, Development}

\begin{abstract}
\textit 
The \nomeTrabalho is a suite, that is, a set of multi-platform, integrated systems that through the RestFul architecture communicate through HTTP protocols and thus form the system completely. It is a system for creating budgets and work orders (W.O) online simply, quickly and directly. For this project, the system consists of an API, which provides services, business rules and data access, developed in JavaScript with NodeJS with PostgreSQL database. A web client, developed in Html5, Css3 and JavaScript, using Aurelia framework 1.0.0 to be the administrative console of the system, in short, will be the communication interface with the API for administration, creation and manipulation of budgets and work orders. A mobile client developed in native Android that will be made available to the customer (human), in that case, a person who will do a service on your vehicle in an automotive center that will use the system. And through the application, you can follow the steps and status of the work order. You will have the option to generate maintenance reports already performed on your vehicles, receive notice notifications when an active work order is closed. The system will not cover the administrative/financial part of the business, it will only count parts, services, customers, vehicles, budgets that can be converted into a service order for a (human) customer's vehicle. The focus of the work will be the integration between the different platforms, systems architecture in the different environments and the relation between them in a homogeneous and transparent way.
\end{abstract}